Pillar 1 - Sequential Pattern Mining

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
use ceiling(grade) instead of round(grade)

  # Spread along rounded grades
  mutate(
    Round_grade = round(Grade, 0),
    Values      = TRUE
    ) %>%
  spread(
    key   = Round_grade, 
    value = Values
    ) %>%

@@

  # Gather along rounded grades
  gather(
    key   = Grade_round,
    value = X,
    `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, 
    na.rm   = TRUE, 
    convert = TRUE
    ) %>%
  select(
    -X
    )%>%

  # Identifying item
  mutate(
    item_G = paste(item, Grade_round, sep = "_")
    )
```
### Additional General Dataframes for courses
#### Transcript with Preceding courses per student
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    course_all  = paste(unique(d_transactions$item), collapse = " "),
    course_all  = str_split(course_all, pattern = " "),

@@

# Probability of taking a course
d_support_take <- d_transactions %>%
  distinct(
    item,
    sequenceID
    ) %>%
  count(
    item
    ) %>%
  mutate(
    rate.take = n / n_students,
    rate.not  = 1 - rate.take)

# Probability of failing, having a low grade, having a grade less than x per course
d_support <- d_transactions %>%
  mutate(
    grade_round = round(Grade)
  ) %>%
  group_by(
    item
    ) %>%
  summarise(
    rate.fail = mean(PF == "fail"),
    rate.low  = mean(HL == "low"),
    rate.0    = mean(grade_round <= 0),
    rate.1    = mean(grade_round <= 1),
    rate.2    = mean(grade_round <= 2),
    rate.3    = mean(grade_round <= 3),
    rate.4    = mean(grade_round <= 4),
    rate.5    = mean(grade_round <= 5),
    rate.6    = mean(grade_round <= 6),
    rate.7    = mean(grade_round <= 7),
    rate.8    = mean(grade_round <= 8),
    rate.9    = mean(grade_round <= 9),
    rate.10   = mean(grade_round <= 10)
    )

>>>>

  # Spread along rounded grades
  mutate(
    grade_ceil = ceiling(Grade),
    Values     = TRUE
    ) %>%
  spread(
    key   = grade_ceil, 
    value = Values
    ) %>%

@@

  # Gather along rounded grades
  gather(
    key   = grade_ceil,
    value = X,
    `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, 
    na.rm   = TRUE, 
    convert = TRUE
    ) %>%
  select(
    -X
    ) %>%

  # Identifying item
  mutate(
    item_G = paste(item, grade_ceil, sep = "_")
    )
```
### Additional General Dataframes for courses
#### Transcript with Preceding courses per student
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    course_all  = paste(unique(d_transactions$item), collapse = " "),
    course_all  = str_split(course_all, pattern = " "),

@@

# Probability of taking a course
d_support_take <- d_transactions %>%
  distinct(
    item,
    sequenceID
    ) %>%
  count(
    item
    ) %>%
  mutate(
    rate.take = n / n_students,
    rate.not  = 1 - rate.take
    )

# Probability of failing, having a low grade, having a grade less than x per course
d_support <- d_transactions %>%
  group_by(
    item
    ) %>%
  summarise(
    rate.fail = mean(PF == "fail"),
    rate.low  = mean(HL == "low"),
    rate.0    = mean(Grade <= 0),
    rate.1    = mean(Grade <= 1),
    rate.2    = mean(Grade <= 2),
    rate.3    = mean(Grade <= 3),
    rate.4    = mean(Grade <= 4),
    rate.5    = mean(Grade <= 5),
    rate.6    = mean(Grade <= 6),
    rate.7    = mean(Grade <= 7),
    rate.8    = mean(Grade <= 8),
    rate.9    = mean(Grade <= 9),
    rate.10   = mean(Grade <= 10)
    )
